\documentclass[a4paper, 11pt]{letter}
\usepackage{hyperref}
\addtolength{\hoffset}{-2cm}
\addtolength{\voffset}{-1.25cm}
\addtolength{\textwidth}{4cm}
\addtolength{\textheight}{3cm}

\signature{Dr. Huang, Ruihong}
\address{Humboldt Universit\"at zu Berlin \\ 
Institute for Statistics and Econometrics \\ 
Spandauer Str. 1  \\
10178 Berlin}
\begin{document} 
\begin{letter}{%
Recruitment Team\\
Deutsche B{\"o}rse Group\\
Recruitment / 50016757 \\
60485 Frankfurt} 
\opening{\textbf{\large{Application for Data Warehouse Specialist}}\\
\vspace{-5pt}\\ Dear Recruitment Team}
As an enthusiastic data miner, I am very interested in the position as a data warehouse specialist. During the five-year research on high-frequency order book data, my knowledge on econometrics and skills on programming have developed to the strong capacity of statistically modelling on financial data. Specifically, I am able to quickly retrieve the information from irregular and huge data sets, build suitable statistical models, and estimate them efficiently by using high-performance computation techniques. Personally, I think this capacity is essential for a successful career as a financial data specialist and therefore believe myself to be a strong, qualified candidate for your job opening.     

Moreover, as a researcher working on Linux platform for eight years and the main developer of data project LOBSTER (\url{http://lobsterdata.com}), I have acquired many programming skills perfectly fitted to your job requirements. In particular, 
\begin{enumerate}
  \item I frequently use shell and Python scripts in my daily research tasks.
  \item I can proficiently program with C++ and Java, and manage my codes by Git.
  \item I have practical experience on working with MySQL data base.
  \item I have deep understanding on math software, such as R and Matlab, and am able to program them with C or Java.
  \item I can pick up a new programming language in just a few days.
\end{enumerate}
I welcome the opportunity to visit with you about this position. My CV has been uploaded, per your instructions. Thanks again for your consideration.
 
\closing{Yours Faithfully,}
 
 
\end{letter}
 
\end{document}



