\documentclass[a4paper, 11pt]{letter}
\usepackage{hyperref}
\addtolength{\hoffset}{-2cm}
\addtolength{\voffset}{-1.25cm}
\addtolength{\textwidth}{4cm}
\addtolength{\textheight}{3cm}

\signature{Dr. Huang, Ruihong}
\address{Karl-Marx Allee 48 \\
10178 Berlin}
\begin{document} 
\begin{letter}{%
Zalando GmbH} 
\opening{\textbf{\large{Application for Quantitative Analyst in Data Intelligence}}\\
\vspace{-5pt}\\ Dear Madam and Sir,}
As an enthusiastic data miner, I am very interested in the position as a quantitative analyst in data intelligence. During the five-year research on high-frequency financial data with nanosecond time stamps, my knowledge on econometrics and skills on programming have been developed to the strong capacity of statistically modelling on the huge data set. Specifically, I am able to quickly retrieve the information from irregular data, build suitable statistical models, and estimate them efficiently by using high-performance computation techniques. Personally, I think this capacity is essential for a successful career as a data specialist and therefore believe myself to be a strong, qualified candidate for your job opening.     

Moreover, as an experienced researcher working on Linux platform for eight years and one of the main developers of data project LOBSTER (\url{http://lobsterdata.com}), I have acquired many skills perfectly fitted to your job requirements. In particular, 
\begin{enumerate}
  \item I hold a Doctoral degree (graduated \emph{summa cum laude}) in Econometrics . I have rich research experience in both econometric analysis and machine learning.
  \item I have deep understanding on math software, such as R and Matlab, and am able to program them with C or Java.
  \item I frequently use Python and shell scripts in my daily research tasks.
  \item I can proficiently program in C++ and Java, and manage my codes by Git.
  \item I have practical experience on working with MySQL database via R and Python.
  \item I feel very comfortable to work in a team and happy to communicate with other team members.
\end{enumerate}
I welcome the opportunity to visit with you about this position. My CV has been uploaded, per your instructions. Thanks again for your consideration.
 
\closing{Yours Faithfully,}
 
 
\end{letter}
 
\end{document}



