\documentclass[a4paper, 11pt]{letter}
\usepackage{hyperref}
\addtolength{\hoffset}{-2cm}
\addtolength{\voffset}{-1.25cm}
\addtolength{\textwidth}{4cm}
\addtolength{\textheight}{3cm}

\signature{Dr. Huang, Ruihong}
\address{3 Selwyn Crescent, \\
Welling \\ 
DA16 2AP \\
United Kingdom}
\begin{document} 
\begin{letter}{%
    Vattenfall AB} 
\opening{\textbf{\large{Application for Quantitative Researcher (Algorithmic Trading Analyst)}}\\
\vspace{-5pt}\\ Dear Madam and Sir,}
I am interested in this position as a quantitative researcher in your team, and believe that myself is a good fit to the role.

I have been working as a quantitative researcher in algorithmic execution since 2013, covering most perspectives of algorithmic trading, e.g. transaction cost analysis, execution strategies and smart order router. In recent years, I have coordinated market data, IT and quantitative team, building an Alpha-enhanced execution framework in Advanced Execution Services (AES) Credit Suisse. The primary result of A/B test by Portfolio Trading desk shows that, the short-term alpha signal (proposed by me) improves the VWAP algo performance against the market VWAP by approximately 20\%.

This is just the latest achievement in my career. Indeed, most of my researches have been implemented and used in products in variant places. Personally, I believe the following factors are keys for making things happen,  
\begin{description}
    \item[Clear research objective] I always spent a lot of time on identifying and clarifying the practical target with stakeholders before starting my research;
    \item[Simple solution] Although I typically tried out many methods in my research, I would carefully balance the complexity and performance when proposing a solution, preferring a simple solution than a complex one unless the performance was substantially different;
    \item[Speaking other's language] With a computer science education background, I could pick up a new IT technology quickly when it was suggested by developers, and then translated my model to a development specification with the new technology in consideration;
    \item[Honest to stakeholders] The new algo might not work as expected at the beginning. When it's the case, I would raise the flag to the traders as soon as possible, so we could investigate the negative outlier together, identify the issue and resolve it. 
\end{description}

I sincerely look forward to talking to you on my experience and my thoughts on execution strategies. Hopefully, I could get the chance to work with you and make more great things happen.  

 
\closing{Yours Sincerely,}
 
 
\end{letter}
 
\end{document}



