%        File: main.tex
%     Created: Thu Jul 01 07:00 AM 2010 U
% Last Change: Thu Jul 01 07:00 AM 2010 U
%
\documentclass[a4paper,10pt]{article}
\addtolength{\hoffset}{-2cm}
\addtolength{\voffset}{-1.25cm}
\addtolength{\textwidth}{3cm}
\addtolength{\textheight}{3.5cm}
\addtolength{\footskip}{-0.5cm}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{url}
\usepackage{xtab}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{array}	
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{datetime}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{pifont}

\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}
\begin{document}
\newcommand{\HU}[0]{Humboldt Universit\"at zu Berlin}
\titleformat{\section}{\normalfont\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\normalsize\bfseries}{\ding{108}}{1em}{}
\newenvironment{idesc}{\begin{description}[font=\hspace{1em}\ding{249}~\scshape\bfseries]}{\end{description}}

\renewcommand\labelitemi{\ding{249}}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand\footrule{\begin{minipage}{1\textwidth}
        \vspace{1em}
\hrule width \hsize height 2pt \kern 1mm \hrule width \hsize   
\end{minipage}\par}
\pagestyle{fancy}
\lfoot{\monthyear\today}
\cfoot{Ruihong Huang}
\rfoot{Page \thepage\ of \pageref{LastPage}}
\begin{tabular}[h]{p{0.25\textwidth}p{0.6\textwidth}}
    &\vspace{1pt}\large{\textbf{Dr. Huang, Ruihong}\newline
  \vspace{-8pt} \newline
Tel: +44 74 7399 9621  \newline
Email: \verb|ruihong.huang@gmail.com| } \\
\end{tabular}\\
\rule[5pt]{1\textwidth}{1pt}\par
\setlength{\tabcolsep}{10pt}
\setlength{\extrarowheight}{7pt}
\section{PROFESSIONAL EXPERIENCE}
\subsection{Founder \& Director, Vonde Consulting Ltd., UK \hfill 01/2020 -- present}
\begin{idesc}
\item[Active portfolio construction and statistical abitrage] based on technical signals and high frequency econometric models, using crypto tick-level market data; 
\item[High-frequency crypto trading and backtesting platform] using tick-level data, developed in Python and C++ with proper functional and unit tests, deployed by docker containers;
\item[Efficient backtesting system for low-frequency trading strategies] as a contractual project for a hedge fund, using level 3 market data, developed in Scala using Spark, deployed on AWS EMR;
\item[Water level prediction neural network] developed in Python using Tensorflow, trained on Tencent cloud, deployed for three cities in China.
\end{idesc}
\subsection{Founder \& Head of Development, frischdaten UG, Germany  \hfill 04/2015 -- present}
\begin{idesc}
    \item[LOBSTER data engine] constructing NASDAQ order book and order flow,  using TotalView-ITCH (level 3 market data stream), developed in Java 7.
\end{idesc}
\subsection{Director, AES Credit-Suisse, UK \hfill 07/2020 -- 04/2022}
\begin{idesc}
    \item[Signal enhanced execution strategies] adjusting schedule-based execution algo, such as VWAP, by directional signals;
    \item[Desk daily cover] including quant guidance for dev and data teams, research advice for junior quants, algo advice and customisation for clients. 
\end{idesc}
\subsection{Vice President, SMAD Barclays, UK \hfill 08/2018 -- 11/2019}
\begin{idesc}
\item[Execution strategy enhancements] including customisable-titled VWAP, impact model for SOR;
\item[Desk daily cover] including TCA reports, algo advice for clients.
\end{idesc}
\subsection{Vice President, AES Credit-Suisse, UK \hfill 07/2016 -- 08/2018}
\begin{idesc}
\item[Commodities intra-day volume regime shift model] detecting volume curve break points using historical data;   
\item[Adaptive VWAP] choosing the best VWAP sub-strategies based on client order characteristics in trading time using a machine learning model;
\item[New behavior of liquidty-seeking strategy] using a configurable continuous response function for Guerrilla algo.
\end{idesc}
\subsection{Associate Director,  Electronic Trading UBS, UK \hfill 11/2013 -- 07/2016} 
\begin{idesc}
\item[Pre-trade costs model] using an exponential kernel, providing a significant improvement on the pre-trade estimation;  
\item[Stop-loss alert model] triggering an alarm when a particular stop-loss order likely causes a intra-day market turbulence;  
\item[Dark IOC routing study] analyzing the liquidity gain and loss of SOR ALP tactics, suggesting a dynamic control on taking the liquidity from the dark pools. 
\end{idesc}
\subsection{Scientific Employee,  QPL Deutsche Bank, Germany \hfill 02/2008 -- 07/2011} 
\begin{idesc}
\item[Financial econometric models] for the limit order book and the order flow.
\end{idesc}

\section{EDUCATIONS AND DEGREES}
\subsection{Doctorate, Humboldt Universit\"at zu Berlin, Germany \hfill 02/2008 -- 02/2012}
\begin{idesc}
\item[Applied econometric models] on high frequency limit order book, order flow and dark liquidity using ultra-high-frequency level 3 market data;
\item[Graded as \emph{summa cum laude}] recognising my extraordinary academic achievements.
\end{idesc}
\subsection{Master student, Royal Inst. of Tech. (KTH), Sweden \hfill 09/2006 -- 02/2008}
\begin{idesc}
\item[Applied mathematics] focusing on numerical methods for PDEs and the high-performance computation.
\end{idesc}
\subsection{M.Sc., University of Copenhagen, Denmark \hfill 04/2004 -- 12/2007}
\begin{idesc}
\item[Economics] including courses of macro, micro-economics and econometrics etc., and a thesis on derivative pricing with L\'{e}vy processes.  
\end{idesc}

\section{PUBLICATIONS}
\begin{itemize}
\item Shen, Y. and R. Huang (2014) ``Risk-averse reinforcement learning for algorithmic trading'', Conference on Computational Intelligence for Financial Engineering \& Economics (CIFEr), 2014 IEEE.
\item Hautsch, N. and R. Huang (2012), ``The market impact of a limit order'', Journal of Economic Dynamics and Control, 36, 501 – 522.
\item  Hautsch, N. and R. Huang (2012), ``Limit order flow, market impact and optimal order sizes: Evidence from NASDAQ TotalView-ITCH data'' in: ``Market Microstructure: Confronting Many Viewpoints'', F. Abergel, J.-P. Bouchaud, T. Foucault, C. Lehal, M. Rosenbaum (eds.), Wiley Intersciences.
\item Hautsch, N. and R. Huang (2012), ``On the dark side of the market: Identifying and analyzing hidden order placements'' Discussion Paper 2012-4, CRC 649, \HU.
\item  Huang, R. and T. Xiao (2012), ``How much can hidden liquidity improve the trading price'' Working Paper, \HU\ and Harvard University.
\item Huang, R. and T. Polak (2011), ``LOBSTER: Limit order book reconstruction system'' Working Paper, \HU.
\end{itemize}

\section{PROGRAMMING  SKILLS }
\begin{itemize}
    \item \textbf{Python} at professional level, using Numpy, Pandas and Scikit-learn for research purpose, integrating C++ libraries using Cython, familiar with Unit Test (including Mock) and type hint, strictly following PEP~8 coding style;
    \item \textbf{GIT and Docker} at professional level, using daily in development and deployment; 
    \item \textbf{C++} at experienced level, familiar with GoogleTest for developing reliable libraries;
    \item \textbf{SQL} at experienced level, familiar with \textbf{MySQL, PostgreSQL} and  \textbf{TimescaleDB};
    \item \textbf{Linux user} with 20-year experience, familiar with most of the common tools;
    \item \textbf{Other programming languages and tools} including Matlab (10+ years), Rust, Java, Scala, KDB+/q, R, OneTick, Apache Spark and Redpandas/Kafka. 
\end{itemize}
\end{document}
